\documentclass{beamer}

\input{MathMacros}

% packages
\usepackage{beamerthemesplit}
\usepackage{enumerate}
\usepackage{amssymb}
\usepackage[all,cmtip]{xy}
\usepackage[mathscr]{eucal}
\usepackage[natbib=true,style=authoryear,backend=bibtex,useprefix=true]{biblatex}
\addbibresource{reading.bib}
\usepackage{graphicx,color}
\usepackage[normalem]{ulem}

\title{Git Ritual}
\author{Reuben Brasher}
\date{\today}

\begin{document}

\frame{\titlepage}

\section[Outline]{}
\frame{\tableofcontents}

\section{Why?}

\frame
{
   \frametitle{Why?}

    Why git? Why PRs? Why the ritual?

    \

    \texttt{
    git clone <my-fancy-project>
    }

}

\frame
{
   \frametitle{Why?}

    Why git? Seriously?

    \

    \texttt{git clone <my-fancy-project>}

    \

    Because we said so.
}

\frame
{
   \frametitle{Why?}

    Why git? Seriously?

    \

    \texttt{
    git clone <my-fancy-project>
    }

    \

    \sout{Because we said so.}

    Because you said you would.

    Because millions of people do.

    Because it works.

    Because it is powerful.

}

\frame
{
   \frametitle{Courage}

    You can be fearless!

   \begin{itemize}
      \item<1-> You can change

      \item<2-> You can change back

      \item<3-> You can delete

   \end{itemize}

}

\frame
{
   \frametitle{Collaborative vs. Individual}

    You are not the only person in the world.

    Your friends love you, but they do not have time to read all of your code and docs.

   \begin{itemize}
      \item<1-> PR and review

      \item<2-> History and blame

      \item<3-> Overall metrics

      \item<4-> Raise awareness of your work

   \end{itemize}

}

\section{First steps}

\frame
{
   \frametitle{Establish an account}

    Use a registered email from your organization.
}

\frame
{
   \frametitle{Local identity}

   \texttt{git config --global user.name "Your Name"}
   \texttt{git config --global user.email "your@email.com"}

}

\frame
{
   \frametitle{SSH keys}

   \texttt{ssh-keygen -t ed25519 -C "your\_email\@example.com"}

   Please use a passphrase!

   \texttt{cat \~/.ssh/id\_ed25519.pub}

}

\section{Next steps}


\frame
{
   \frametitle{Clone existing repo}

   \texttt{git clone <my-fancy-project>}

}

\frame
{
   \frametitle{Create from scratch}

   Always have .gitignore

    Always have README.md

    Strongly consider LICENSE

    Note that you are not just publishing current state, but commit history

    Initially set repo as private

}

\frame
{
   \frametitle{Branch protection}

   Branch protection!
}

\section{Day to day}

\frame
{
   \frametitle{Basic work}

Always work in a branch

\texttt{git checkout -b rb/my\_cool\_feature}

Commit often

Commit changes to files in a descriptive manner

Commit may reference Jira
}


\frame
{
   \frametitle{PR}

   \texttt{git push}

   Good commit description

   Reference a jira ticket (No ticket?)

   Request a review

}

\frame
{
   \frametitle{Merge PR}

    Resolve conflicts

    Rebase or merge locally

    Make sure tests continue to pass
}

\frame
{
   \frametitle{Feature branches?}

   Be cautious.
}



\begin{frame}[t,allowframebreaks]
\frametitle{References}
\printbibliography
\end{frame}

\end{document}
